Text Detection and Chinese Character Recognition in Natural Scene Images via Pre-trained Vision and Language Models

### 2020-11-12 A-BasicCommom/CVPR2021/cvpr_apsp.tex
1. comfort all papers.

%%%%%%%%% ABSTRACT
\begin{abstract}
  For the shortest path calculation of the all-pairs nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(2\log{n}n^3)\).
  The proposed all-pairs shortest path algorithm, which has an improved lower time-bound \(O(14n^3)\), leverages matrix sparseness judgment, convergence judgment, distance product with matrix multiplication, association law for distance product,
  scale-free characteristics of the social networks degrees and precision limit of floating point operations on the modern hardware.
  Tested on the movie actors' social network dataset, the algorithm has an improvement of 39\% to 36.2 times in performance on the CPU/GPU platforms comparing to Alon \etal's all-pairs shortest path algorithm.
\end{abstract}

@@

In recent years, driven by the Asian film industries such as China and India, the global box office has maintained a steady growth trend, and with the rapid development of social network applications, more and more actors use social networks for work communication.
Therefore, the social network has become an important tool for film distribution, marketing, promotion, and an important medium for film actors and fans to interact.
Previous studies have lacked research on actors' social networks, PageRank, an existing node influence algorithm, is not accurate in evaluating social network influence.
Social network feature measurement is an important task in social network data mining, some network characteristics, such as betweenness and closeness, need to calculate the distances between nodes.
As a result, efficient calculation of the shortest path is one of the key problems in social network measurement.
There was Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem} algorithm for calculating node distances, Aho and Hopcroft~\cite{aho1974design} proved that distance product is homogenous to matrix multiplication,
Alon \etal~\cite{alon1997exponent} proposed an algorithm to calculate distance product by matrix multiplication, Zwick~\cite{zwick2002all} optimized distance product using fast matrix multiplication,
and Garbow and Winograd~\cite{garbow1985scaling} proposed an algorithm for distance product using matrix multiplication with element bound.
From time-bound of matrix multiplication, Strassen~\cite{strassen1969gaussian}, Coppersmith and Winograd~\cite{coppersmith1987matrix}, Davie and Andrew~\cite{davie2013improved}, Le Gall~\cite{le2014powers} proposed the block matrix multiplication with time-bound of \(O(n ^ {2.807})\), \(O(n^{2.376})\), \(O(n^{2.374})\), \(O(n^{2.373})\).
Lam \etal~\cite{lam1991cache} proposed that the progressive time complexity of matrix multiplication with a cache block size of $\Bbb B$ is \(O({2n^3 \over \Bbb B}+{n^2})\),
and Goto and Geijn~\cite{goto2008anatomy} proposed a new library, OpenBLAS, which has a higher cache hit rate and improved time cost in matrix computation on X86 CPU, compared to modern BLAS libraries, such as Intel MKL v8.1.1, ESSL v4.2.0, and ATLAS v3.7.11.
From point of view of matrix sparseness of network adjacent matrix, for sparse matrix multiplication, SciPy and CuPy use SciPy-sparse and CuPy-cuSparse to achieve efficient sparse matrix multiplication on CPU and GPU.
For dense matrix multiplication, NumPy, SciPy, CuPy, and ND4J use OpenBLAS, cuBLAS, and other libraries to achieve efficient block matrix multiplication on CPU and GPU.
Therefore, a feasible method for calculating the shortest path of full node pairs is: represents the network by adjacent matrix, then makes all matrix elements exponential, computes matrix multiplication, and finally takes the logarithm of matrix elements.
This procedure is called a distance product epoch.
Iterate several times to get all-pairs shortest path result.
Further, the analysis time complexity of the distance product calculation and iteration of each epoch.
For time complexity of the distance product, matrix multiplication is the most complex sub-procedures.

@@

On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
On the computer hardware, compared the $8508\times 8508$ matrix multiplication time cost.
The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library, it takes only 4 seconds.
The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
Therefore, the distance product algorithm proposed by Zwick with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.

@@

\subsection{The Shortest Path Algorithm with Joint Sparseness Judgment and Convergence Judgment}

@@

Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table 1.
$Power-LawBound(a-f)$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.

@@

This paper discussed a novel algorithm in the all-pairs shortest path computation tasks, using distance product association law.
The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({2\log{n}n^3\over \Bbb B})\).
To strengthen the conditions, on the scale-free social networks, for the precision limit of floating point operation on hardware,
additional condition on the social network diameter is added to avoid overflow in the floating point operations,
the analysis showed that the algorithm has a lower time-bound \(O({14n^3\over \Bbb B})\).
With a hypothesis that all the social networks have limit diameters, I proposed a novel algorithm,
which leverages matrix sparseness judgment, and calculation convergence judgment.
\textbf{Power-Law} refers to the network node degrees conforming to the characteristics that social networks power-law distribution,
and \textbf{Bound} refers to the precision limit for diameters of floating point arithmetic operations on hardware.
The experimental results show that \textbf{Power-LawBound} algorithm improves time performance by 39\% to 36.2 times
on CPU/GPU hardware compared to Alon \etal's algorithm.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
  For the shortest path calculation of the all-pairs nodes in networks, Alon \etal~\cite{alon1997exponent} proposed an algorithm with matrix multiplication.
  In this paper, with the distance product association law and block matrix multiplication, all-pairs shortest path algorithm has a lowered time-bound of \(O(2\log{n}n^3)\).
  The proposed all-pairs shortest path algorithm, which has an improved lower time-bound \(O(14n^3)\), leverages the following improvements:
  matrix sparseness judgment, convergence judgment, distance product by matrix multiplication, association law for distance product,
  scale-free characteristics of the social networks degrees and the precision limit of floating point operations on the modern hardware.
  Comparing to Alon \etal's algorithm, the algorithm has an improvement of 39\% on CPU and 36.2 times on GPU on the movie actors' social network dataset.
\end{abstract}

@@

In recent years, driven by the Asian film industries, such as China and India, the global box office has maintained a steady growth trend.
With the rapid development of social network applications, more and more actors use social networks for work communication.
Therefore, the social network has become an important tool in film distribution, marketing, promotion, and an important medium for film actors and fans to interact.
Previous studies are lack of research on actors' social networks, PageRank, a widely used web page influence algorithm, is not accurate in evaluating social network influence.
Social network feature measurement is an important task in social network data mining, some network characteristics, such as betweenness and closeness, need to calculate the distances between nodes.
As a result, efficient calculation of the shortest path is one of the key problems in social network measurement.
There was Floyd-Warshall~\cite{floyd1962algorithm,warshall1962theorem} algorithm for calculating node distances, Aho and Hopcroft~\cite{aho1974design} proved that distance product is homogenous to matrix multiplication,
Alon \etal~\cite{alon1997exponent} proposed an algorithm to calculate distance product by matrix multiplication, Zwick~\cite{zwick2002all} optimized distance product using fast matrix multiplication,
and Garbow and Winograd~\cite{garbow1985scaling} proposed an algorithm for distance product using matrix multiplication with element bound.
From time-bound of matrix multiplication, Strassen~\cite{strassen1969gaussian}, Coppersmith and Winograd~\cite{coppersmith1987matrix}, Davie and Andrew~\cite{davie2013improved}, Le Gall~\cite{le2014powers} proposed the block matrix multiplication with time-bound of \(O(n ^ {2.807})\), \(O(n^{2.376})\), \(O(n^{2.374})\), \(O(n^{2.373})\).
Lam \etal~\cite{lam1991cache} proposed that the progressive time complexity of matrix multiplication with a cache block size of $\Bbb B$ is \(O({2n^3 \over \Bbb B}+{n^2})\),
and Goto and Geijn~\cite{goto2008anatomy} proposed a new library, OpenBLAS, which has a higher cache hit rate and improved time cost in matrix computation on X86 CPU, compared to modern BLAS libraries, such as Intel MKL v8.1.1, ESSL v4.2.0, and ATLAS v3.7.11.
From point of view of matrix sparseness of network adjacent matrix, for sparse matrix multiplication, SciPy and CuPy use SciPy-sparse and CuPy-cuSparse to achieve efficient sparse matrix multiplication on CPU and GPU.
For dense matrix multiplication, NumPy, SciPy, CuPy, and ND4J use OpenBLAS, cuBLAS, and other libraries to achieve efficient block matrix multiplication on CPU and GPU.
Therefore, a feasible method for calculating the shortest path of full node pairs is: represents the network by adjacent matrix, then makes all matrix elements exponential, computes matrix multiplication, and finally takes the logarithm of matrix elements.
This procedure is called a distance product epoch.
Iterate several times to get all-pairs shortest path result.
Further, the analysis time complexity of the distance product calculation and iteration of each epoch.
For time complexity of the distance product, matrix multiplication is the most complex sub-procedures.

@@

On the actors' social network, this paper implements Strassen block matrix multiplication, Copper-Winograd block matrix multiplication, and OpenBLAS matrix multiplication.
On the computer hardware, compared the $8508\times8508$ matrix multiplication time cost.
The block matrix multiplication based on Strassen and Coppersmith-Winograd takes 6 seconds for one iteration of matrix multiplication, and with the OpenBLAS library, it takes only 4 seconds.
The performance of optimized cache block matrix multiplication, such as the OpenBLAS matrix computation library, is higher than Strassen and Copper-Winograd block matrix multiplication algorithm.
Therefore, the distance product algorithm proposed by Zwick with OpenBLAS block matrix multiplication is better than the distance product algorithm with Strassen and Coppersmith-Winograd.

@@

\subsection{Algorithm with Joint Sparseness Judgment and Convergence Judgment}

@@

Firstly, compared to Floyd-Warshall algorithm implemented on CPU, the Alon \etal algorithm implementation with matrix multiplication of block cache optimization on GPU has a time performance improvement, see Table (1).
$Power-LawBound(a-f)$ shows that using different libraries on CPU/GPU, the proposed algorithm has significant performance improvement over Alon \etal algorithm.

@@

This paper discussed a novel algorithm in the all-pairs shortest path computation tasks, using distance product association law.
The time-bound of Alon \etal distance product algorithm with block matrix multiplication is \(O({2\log{n}n^3\over \Bbb B})\).
To strengthen the conditions, on the scale-free social networks, for the precision limit of floating point operation on hardware,
additional condition on the social network diameter is added to avoid overflow in the floating point operations,
the analysis showed that the algorithm has a lower time-bound \(O({14n^3\over \Bbb B})\).
With a hypothesis that all the social networks have limit diameters, I proposed a novel algorithm,
which leverages matrix sparseness judgment, and calculation convergence judgment.
\textbf{Power-Law} refers to the network node degrees conforming to the characteristics that social networks power-law distribution,
and \textbf{Bound} refers to the precision limit for diameters of floating point arithmetic operations on hardware.
Comparing to Alon \etal's algorithm, the experimental results show that \textbf{Power-LawBound} algorithm has an improvement of 39\% on CPU and 36.2 times on GPU on the movie actors' social network dataset.

### 2020-11-12 A-BasicCommom/CVPR2021/cvpr_classification.tex
1.add a new Paper.
1. comfort all papers.

  Image classification and categorization are essential to the capability of telling the difference between images for a machine.
  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

@@

My approach consists of a pre-training state followed by a fine-tuning stage.
In pre-training, I use BERT objectives and the sequence Transformer architecture to predict language tokens.

@@

\par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands of news in 10 domains.

\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
The \textit{Case-2} dataset annotated civil and criminal cases, and the \textit{Case-4} dataset annotated by civil, criminal, intellectual property, and administrative cases.
The \textit{Case-2} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Case-4} dataset has $34789$ training documents and $2013$ test documents.

\par From table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
the test accuracy exceeds the other popular machine learning algorithms.
Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|r|}
\hline
Language Model 	& Dataset & Accuracy \\
\hline\hline
RoBERTa-wwm-ext-large & Case-2	&	99.80\% \\
RoBERTa-wwm-ext-large & Case-4	&	99.76\% \\
RBTL3  & Case-4	&	96.35\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on different datasets in the document classification task.}
\end{table}
%-------------------------------------------------------------------------

@@

I design simple classification models without too many layers, as Figure (1) shows.
And use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
The model architecture has seven functional layers:

@@

\par The CIFAR-10 dataset contains 60000 color images with a resolution of 32x32 in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
then encode other meta-data if provided, as a sequence of ASCII characters.
In the Concatenation layer, the pixel-channel value and metadata are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
and put a $\textbf{[SEP]}$ token between channel values and metadata, put a special token of $\textbf{[SEP]}$ at the end.
In the Trim layer, due to the limit on the max sequence of the BERT language model, a sequence larger than $512$ needs to be trimmed before sending it to the BERT model.
Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contains the first 255 red-channel value,
some blue-channel value, and all the meta value in common cases.
In the Encoder layer and the Embedding layer, trimmed sequence of values are encoded by BERT-like models,
and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation (2), is used.
In the Output layer, the classification label of the image is feed in the model.

@@

\subsection{The Mask Token for Test}

\par It is intuitive for the model to use both the channel values and the metadata during the training phase.
For the CIFAR-10 and CIFAR-100 dataset, the metadata is the filename of the images, which can be treated as the supervised description of the image.
Peek some the filenames, \eg \textit{wagon\_s\_001343.png}, \textit{banana\_boat\_s\_001615.png}, and \textit{delivery\_truck\_s\_001529.png},
and it is beneficial for the classification model to understand the supervised descriptive information for the image.

\par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
the metadata, which is the filename in this case, to the image class
which makes it is unfair to compare the performance with other image classification models.
Thus, to be more objective and fair, I add a preprocess for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
ASCII character of the filename then feeds into the model to do the inference.

@@

@@

Use the proposed model, and I tried different pre-trained language models to see the impact on classification accuracy.
From the table-2, for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
however, its training cost grows for the larger language model.
For the same fine-tuned language model, classes number has some impact on the accuracy,
the fewer classes the dataset has, the more accurate results the model can achieve.

>>>>

  Image classification and categorization are essential to the capability of telling the difference between images for a machine
  which is initially designed for vision purposes.
  As \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers became popular in many tasks of natural language processing recent years,
  it is intuitive to use these pre-trained language models for enhancing the computer vision tasks, \eg image classification.
  In this paper, by encoding image pixels using pre-trained transformers, then connect to a fully connected layer,
  the classification model outperforms the Wide ResNet model and the linear-probe iGPT-L model,
  and achieved accuracy of $99.60\%\sim99.74\%$ on the CIFAR-10 image set and accuracy of $99.10\%\sim99.76\%$ on the CIFAR-100 image set.

@@

My approach consists of a pre-training stage followed by a fine-tuning stage.
In pre-training, I use BERT objectives and the sequence Transformer architecture to predict language tokens.

@@

\par Recall that Kim~\cite{kim2014convolutional} had proved that unsupervised pre-trained language model $word2vec$ and CNN outperformed many other machine learning algorithms,
\eg support vector machines and conditional random field, in many datasets such as movie reviews, Stanford sentiment treebank, and TREC question.
Cui \etal's pre-trained language model, namely RBT3, RBTL3, and RoBERTa-wwm-ext-large, had improved performances over many other machine learning algorithms.
BERT and RoBERTa-wwm-ext-large models both achieved an f1-score of 97.8\% in the THUCNews dataset, which contains 65 thousands news reports in 10 domains.

\par I used RBTL3 and RoBERTa-wwm-ext-large pre-trained language model in two Chinese Judicial datasets, which has 2 and 4 classes.
The \textit{Two-Case} dataset annotated civil and criminal cases, and the \textit{Four-Case} dataset annotated by civil, criminal, intellectual property, and administrative cases.
The \textit{Two-Case} dataset has $19508$ training documents and $2000$ test documents, and the \textit{Four-Case} dataset has $34789$ training documents and $2013$ test documents.

\par From Table (1), by combining the pre-trained language model with fully connected layer as the document classification model,
the test accuracy exceeds the other popular machine learning algorithms.
Therefore, the pixel channels of an image can be properly represented by these pre-trained language models.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|r|}
\hline
Language Model 	& Dataset & Accuracy \\
\hline\hline
RoBERTa-wwm-ext-large & Two-Case	&	99.80\% \\
RoBERTa-wwm-ext-large & Four-Case	&	99.76\% \\
RBTL3  & Four-Case	&	96.35\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of the pre-trained language models on different datasets in the document classification task.}
\end{table}
%-------------------------------------------------------------------------

@@

I design simple classification models without too many layers, as Figure (1) shows,
and use the CIFAR-10 and CIFAR-100 dataset as an example to show the architecture of the model.
The model architecture has seven functional layers:

@@

\par The CIFAR-10 dataset contains 60000 color images with a resolution of $32\times32$ in 10 classes, and the CIFAR-100 dataset has 100 classes containing 600 images each.
Encode the image by the sequence of RGB channel values, in the order of Red-channel, Green-channel, and Blue-channel,
then encode other meta-data if provided, as a sequence of ASCII characters.
In the Concatenation layer, the pixel-channel value and metadata are concatenated, put a special token of $\textbf{[CLS]}$ at the start,
and put a $\textbf{[SEP]}$ token between channel values and metadata, put a special token of $\textbf{[SEP]}$ at the end.
In the Trim layer, due to the limit on the max sequence of the BERT language model, a sequence larger than $512$ needs to be trimmed before sending it to the BERT model.
Keep the first 256 characters and last 256 characters of the concatenated sequence, trimmed result contains the first 255 red-channel value,
some blue-channel value, and all the meta value in common cases.
In the Encoder layer and the Embedding layer, trimmed sequence of values are encoded by BERT-like models,
and get the encoded representation of the token $\textbf{[CLS]}$ as the images' language model embeddings.
In the Feature-Extraction layer, a combination of one dropout layer, one fully connected layer, and one softmax layer, as equation (2), is used.
In the Output layer, the classification label of the image is feed in the model.

@@

\subsection{More Fair Comparison by The Mask Token}

\par It is intuitive for the model to use both the channel values and the metadata in the training phase.
For the CIFAR-10 and CIFAR-100 dataset, the metadata is the filename of the images, which can be treated as the supervised description of the image.
Peek some the filenames, \eg \textit{wagon\_s\_001343.png}, \textit{banana\_boat\_s\_001615.png}, and \textit{delivery\_truck\_s\_001529.png},
and it is beneficial for the classification model to understand the supervised descriptive information for the image.

@@

\par However, in the test phase, if feeding the metadata to the model, people might argue that the model learns only the mapping function from
the metadata, which is the filename in this case, to the image class, which makes it is unfair to compare the performance with other image classification models.
Thus, to be more objective and fair, I add a preprocess step for the metadata in the test phase, using the $\textbf{[MASK]}$ token to replace each
ASCII character of the filename then feeds into the model to do the inference.

@@

Using the proposed model, I tried different pre-trained language models to see the impact on classification accuracy.
From the Table (2), for the same size of a dataset with larger classes, it needs more epochs and training time for the classification model.
For the same RoBERTa language model with different numbers of transformer layers, 24 layers of transformers had better accuracy than 3 layers,
however, its training cost grows for the larger language model.
For the same fine-tuned language model, classes number has positive impact on the accuracy,
the fewer classes the dataset has, the more accurate results the model can achieve.

### 2020-11-12 A-BasicCommom/CVPR2021/cvpr_detrec.tex
1. comfort all papers.

  Detecting and reading text from natural scene images is an essential computer vision tasks.
  Giving the fact that Chinese characters have more tokens than English characters, OCR in Chinese is much harder than English.
  I encode high dimension features extracting from images by ResNet followed by the pre-trained language models of
  \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers,
  then connect to a recurrent neural network layer, and a fully connected layer in the Character Recognize architecture.
  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $71.74\%$ on the Baidu2019 street scene test set.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|r|}
\hline
Model & Dim & Dataset& Epochs & Accuracy \\
\hline\hline
ResNet      & 18 &  ICDAR2015 &50 &	23.67\% \\
ResNet      & 18 &  Baidu2019	  &50 &	56.25\% \\
ResBertNet  & 18+3 & Baidu2019    & 50	&	71.74\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of character detection models on the Baidu Street View 2019 dataset and the ICDAR2015 dataset.
The ResBertNet uses 18 layers of Residual Network and 3 layers of Transformers.}
\end{table}

@@

From Table (1) we can see that, on the ICDAR2015~\cite{karatzas2015icdar} dataset, the ResNet text recognition model has accuracy of 23.67\%,
though the ICDAR2015 test set only contains 92 different English characters, numbers and punctuations,
the ResNet model cannot achieve a satisfactory result after 50 epochs.
It shows that Street Scene View text recognition task is a hard problem and there is no easy way out.
Moreover, the Baidu Chinese street text view dataset contains 4095 different character types.
Compare to the accuracy of 56.25\% on the Baidu2019 street view text dataset, our models have preferable better results.
The reason that the model's outstanding performance lies in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use of extra language corpus of
$5.4$ billions of tokens of wiki data and other resources.
The transformers in the pre-trained language models use multiple layers for representing images and may be used in other Computer Vision task, \eg object detection, gesture prediction.

@@

This paper proposes a novel idea by using pre-trained language models for Chinese scene text detection and recognition.
The finding improves the accuracy in OCR for Chinese street scene, and might improve the accuracy of other language scene detection and recognition.
Tests showed that the proposed model outperforms the ResNet model without augmentation on the image dataset,
the model achieved accuracy of $71.74\%$ on the Baidu 2019 street view text recognition set.

>>>>

  Detecting and reading text from natural scene images is an essential computer vision tasks.
  Giving the fact that Chinese characters have more tokens than English characters, OCR in Chinese is much harder than English.
  I encode high dimension features extracting from images by ResNet followed by the pre-trained language models of
  \underline{B}idirectional \underline{E}ncoder \underline{R}epresentations from \underline{T}ransformers,
  then connect to a recurrent neural network layer, and a fully connected layer in the Character Recognize architecture.
  The proposed recognition model outperforms the ResNet recognition model, and achieved accuracy of $77.24\%$ on the Baidu2019 street scene test set.

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|r|}
\hline
Model & Dim & Dataset& Epochs & Accuracy \\
\hline\hline
ResNet      & 18 &  ICDAR2015     & 50 &	23.67\% \\
ResNet      & 18 &  Baidu2019	  & 30 &	56.25\% \\
ResBertNet  & 18+3 & Baidu2019    & 64	&	77.24\% \\
\hline
\end{tabular}
\end{center}
\caption{Comparision of accuracy of character detection models on the Baidu Street View 2019 dataset and the ICDAR2015 dataset.
The ResBertNet uses 18 layers of Residual Network and 3 layers of Transformers.}
\end{table}

@@

From Table (1) we can see that, on the ICDAR2015~\cite{karatzas2015icdar} dataset, the ResNet text recognition model has accuracy of 23.67\%,
though the ICDAR2015 test set only contains 92 different English characters, numbers and punctuations,
the ResNet model cannot achieve a satisfactory result after 50 epochs.
From the training logs, I can see that the model has converged on a optimal point that after the 30th epoch,
and has no improvement in accuracy afterwards.
It shows that Street Scene View text recognition task is a hard problem and there is no easy way out.
Moreover, the Baidu Chinese street text view dataset contains 4095 different character types.
Compare to the accuracy of 56.25\% on the Baidu2019 street view text dataset, our models have preferable better results.
The reason that the model's outstanding performance lies in the large pre-trained data for BERT, on top of that fine-tuned by RoBERTa, and use of extra language corpus of
$5.4$ billions of tokens of wiki data and other resources.
The transformers in the pre-trained language models use multiple layers for representing images and may be used in other Computer Vision task, \eg object detection, gesture prediction.

@@

This paper proposes a novel idea by using pre-trained language models for Chinese scene text detection and recognition.
The finding improves the accuracy in OCR for Chinese street scene, and might improve the accuracy of other language scene detection and recognition.
Tests showed that the proposed model outperforms the ResNet model without augmentation on the image dataset,
the model achieved accuracy of $77.24\%$ on the Baidu 2019 street view text recognition set.
